### 2020-09-21 LaTeX/sections/abstract.tex
full round edit (#1)

\begin{abstract}
Order-driven exchanges on Ethereum tend to operate in a fully centralized fashion, or with some functionality performed on-chain (\eg loading accounts, order cancelation) and some off-chain functionality (\eg matching orders). Fully on-chain solutions have a superior threat model and were experimented with in the early days of Ethereum, but they have been largely abandoned for performance reasons. As blockchain performance continues to improve (both in research and in practice) and on-chain dealer-based exchanges like Uniswap (an alternative to order-based exchanges) rise in popularity, it seems to be an ideal time to revisit the idea of a fully on-chain order-driven exchange and benchmark what is possible performance-wise. We design and optimize an Ethereum-based call market exchange, \cm, and conduct a variety of experiments to show the current benchmark is around one hundred trade executions per block. We also explore numerous extensions for further improvements.
\end{abstract}

>>>>

\begin{abstract}
Order-driven exchanges on Ethereum tend to operate in a fully centralized fashion, or with some functionality performed on-chain (\eg loading accounts, order cancelation) and some off-chain functionality (\eg matching orders). Fully on-chain solutions have a superior threat model and were experimented with in the early days of Ethereum, but they have been largely abandoned for performance reasons. As blockchain performance continues to improve (both in research and in practice) and on-chain dealer-based exchanges like Uniswap (an alternative to order-based exchanges) rise in popularity, it seems to be an ideal time to revisit the idea of a fully on-chain order-driven exchange and benchmark what is possible performance-wise. We design and optimize an Ethereum-based call market exchange, \cm, and conduct a variety of experiments to show \textblue{the current benchmark is around one hundred trade executions per block}. We also explore numerous extensions for further improvements.
\end{abstract}

### 2020-09-21 LaTeX/sections/appendix.tex
full round edit (#1)

As discussed in Section~\ref{sec:gasrefund}, whether to clean up storage variables or not remains a vital challenge for developers when developing DApps on the Ethereum blockchain--- this is even more crucial for implementation of \cm, as we needed  to choose the best middle ground design model which gives us a satisfactory performance and cost results. For this reason, we believe it it is helpful (both for researchers and developers) to extend our discussion on this topic. First, we discuss the Ethereum's gas model--- (i) what are different gas parameters one needs to take into account when sending a transaction on the Ethereum blockchain, (ii) what is the gas refund, and (iii) and how it is calculated.  Next, we discuss one major challenge, \textit{clearing mappings}, that we faced when implementing \cm on the Ethereum.

@@

To maintain the ETH and ERC20 tokens balances of each trader in \cm, we use one-to-one mappings, \texttt{totalBalance} and \texttt{unavailableBalance}, that map Ethereum addresses to unsigned integers. Note that we need to clear up the entire  \texttt{unavailableBalance} mapping during the orders settlement and clearing phase. However in Solidity, it is not possible to delete the entire mapping without knowing the keys~\footnote{In a Solidity mapping, only individual keys and what they map to can be deleted: https://solidity.readthedocs.io/en/v0.5.12/security-considerations.html}. Here we propose and discuss the landscape of various solutions together with how each method affects the total amounts of gas costs for clearing orders in \cm.

@@

%---------+++++++++++++++++++-----------------
\item \textbf{Generating custom mapping keys.} We can also define a global counter variable and use it as a custom key for the mappings. This counter is incremented \textit{only once} at the end of the matching process. So we only use a new portion of the mapping (and leave the used portion on the Ethereum blockchain) every time the market opens. This solution removes the burden of the gas cost from the \texttt{matchOrders()} function (as discussed in Section~\ref{sec:gasrefund}, leaving the data on chain is cheaper then cleaning it up), however DApp developers are advised to be good citizens of Ethereum and cleanup on-chain data they no longer need.

>>>>

As discussed in Section~\ref{sec:gasrefund}, whether to clean up storage variables or not remains a vital challenge for developers when developing DApps on the Ethereum blockchain--- this is even more crucial for implementation of \cm, as we need to choose the best middle ground design model which gives us optimized performance and cost results. For this reason, we believe it it is helpful (both for researchers and developers) to extend our discussion on this topic. First, we discuss the Ethereum's gas model--- (i) what are different gas parameters one needs to take into account when sending a transaction on the Ethereum blockchain, (ii) what is the gas refund, and (iii) and how it is calculated.  Next, we discuss one major challenge, \textit{clearing mappings}, that we faced when implementing \cm on the Ethereum.

@@

To maintain the ETH and token balances of each trader in \cm, we use one-to-one mappings, \texttt{totalBalance} and \texttt{unavailableBalance}, that map Ethereum addresses to unsigned integers. Note that we need to clear up the entire  \texttt{unavailableBalance} mapping during the orders settlement and clearing phase. However in Solidity, it is not possible to delete the entire mapping without knowing the keys~\footnote{In a Solidity mapping, only individual keys and what they map to can be deleted: https://solidity.readthedocs.io/en/v0.5.12/security-considerations.html}. Here we propose and discuss the landscape of various solutions together with how each method affects the total amounts of gas costs for clearing orders in \cm.

@@

%---------+++++++++++++++++++-----------------
\item \textbf{Generating custom mapping keys.} We can also define a global counter variable and use it as a custom key for the mappings. This counter is incremented \textit{only once} at the end of the matching process. So we only use a new portion of the mapping (and leave the used portion on the Ethereum blockchain) every time the market opens. This solution removes the burden of the gas cost from the \texttt{matchOrders()} function (as discussed in Section~\ref{sec:gasrefund}, leaving the data on chain is cheaper than cleaning it up), however DApp developers are advised to be good citizens of Ethereum and cleanup on-chain data they no longer need.

### 2020-09-21 LaTeX/tables/functions.tex
full round edit (#1)

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
	DepositToken()                           & Deposits ERC20 standard compliant tokens in the call market contract \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
	DepositEther()                           	& Deposits ETH in the call market contract                         			 \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
	OpenMarket()                             & Opens the market                                                    					 \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
	CloseMarket()                            & Closes the market                                                    					\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
	SubmitBid()                              & Inserts the upcoming bid order messages inside the priority queue    \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
	SubmitAsk()                              & Inserts the upcoming ask order messages inside the priority queue    \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
	MatchOrders()                           & Matches the orders against each other                                			\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
	ClaimTokens()                           & Transfers collateralized tokens back to the trader                       			\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
	ClaimEther()                             & Transfers collateralized ETH back to the trader                       			\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
\end{tabular}
\caption{\footnotesize{Primary operations of the call market smart contract.}
\label{tab:callmarket_functions}}
\end{table}

>>>>

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
	depositToken()                           & Deposits ERC20 standard compliant tokens in \cm smart contract \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
	depositEther()                           	& Deposits ETH in \cm smart contract                        			 \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
	openMarket()                             & Opens the market                                                    					 \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
	closeMarket()                            & Closes the market                                                    					\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
	submitBid()                              & Inserts the upcoming bid order messages inside the priority queue    \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
	submitAsk()                              & Inserts the upcoming ask order messages inside the priority queue    \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
	matchOrders()                           & Matches the orders against each other                                			\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
	claimTokens()                           & Transfers collateralized tokens back to the trader                       			\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
	claimEther()                             & Transfers collateralized ETH back to the trader                       			\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
\end{tabular}
\caption{\footnotesize{Primary operations of \cm smart contract.}
\label{tab:cm_functions}}
\end{table}
